Changelog

### 2021-05-22 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection*{Software Patching}
There are two common countermeasures to mitigate side-channel attacks in cryptography libraries. The first approach is to adopt constant time operation when computing the secret data.  It is hard to migrate all the code into a constant-time implementation. The second approach is to use blinding to obfuscate the information that an attacker can retrieve. Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself. Binding values can alter the input to some unpredictable data and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.
\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
\subsubsection*{Randomization}

>>>>

\subsubsection*{Software Patching}
Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks in libraries. The first approach is to adopt unified behavior code when computing the secret data. For example, a control flow leakage happens when different secret inputs lead to different paths. Software can mitigate the leakage by executing both branches and select the result with the bit-wise operations.   However, for exiting code base, it is hard to migrate all the code into a constant-time implementation. The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve. One example is cryptographic blinding. Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself. Binding values can alter the input to some unpredictable data and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.
\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
\subsubsection*{Randomization}
